Bayesian Analysis of Gas-free Galaxies in Simulations I: Reviving Stochasticity

### 2022-10-11 papers/paper-1/paper-1.tex
Update figures to reflect hernquist runs

\textit{Software:} \ketju \citep{rantala17}, \gadget \citep{springel05}, \textsc{Stan} \citep{carpenter17}, NumPy \citep{numpy}, SciPy \citep{scipy}, Matplotlib \citep{matplotlib}, pygad \citep{rottgers20}, Arviz \citep{arviz}.

>>>>

\textit{Software:} \ketju{} \citep{rantala17}, \gadget{} \citep{springel05}, \textsc{Stan} \citep{carpenter17}, NumPy \citep{numpy}, SciPy \citep{scipy}, Matplotlib \citep{matplotlib}, pygad \citep{rottgers20}, Arviz \citep{arviz}.

### 2022-10-11 papers/paper-1/sections/results.tex
Update figures to reflect hernquist runs

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_posterior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}

@@

>>>>

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-H-H-3.0-0.001_posterior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit for highest (fiducial) mass resolution. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}

@@

\begin{figure*}
    \includegraphics{compare_HH_gqs_res.png}
    \caption{\drafting{Comparison of core sersic fit for different mass resolutions. Note the scatter does not seem to decrease with increasing mass resolution, however the distribution modes seem to converge towards something. y-axes should read PDF}}
    \label{fig:cs_mass_compare}
\end{figure*}
